InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Incorporate feedback (#25)
* Added some of the given feedback

* Update paper.tex

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

* deleted subsections

* incorporated review feedback

---------

Co-authored-by: EhrenbruderRoschtbraten <81183139+EhrenbruderRoschtbraten@users.noreply.github.com>

\section{Introduction}
The development of generative Machine Learning models made huge steps forward in the last years, considering the comparison with human crafted artefacts. Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles. Image generating models like Vision Transformer (ViT) already created fake images being reported as real by media. Other news showed artists winning art competitions with generated art. This creates an interest in detecting which texts or images are AI generated and which ones are real images or human-written texts.

Therefore researchers evaluated different approaches to detect fake images and texts. Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e. g. visual object detection, by artificially manipulating real images. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.

@@

\subsection{Generating models}

\subsubsection{Image generating models}

\textbf{Winston AI} is a commercial AI text detector that starts at 18\$ a month. They have two primary methods for checking if a text is AI written. Firstly linguistic analysis analyses every text for characteristics, that are different between human- and AI-generated work. One example characteristic is the repetitiveness, another is Data Training, where the detector saw many AI written texts of one model and learned unique characteristics that this model uses which then can be detected. So this method is more generator-specific. \cite{WinstonAI}

\subsubsection{Text generating models}

@@

\subsubsection{Image detector models}

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset. Swin-Transformer by Microsoft is a new Vision Transformer which makes use of hierarchical windows. This reduces the self-attention to not-overlapping windows of other areas of the image \cite{liu2021swin}.

@@

\subsubsection{Text detector models}

>>>>

\section{Introduction}
The development of generative Machine Learning models made huge steps forward in the last years considering the comparison with human crafted artefacts. Large Language Models (LLM) enable the generation of texts in all kinds of different flavours and styles. Image generative models like Vision Transformer (ViT) already created fake images being reported as real by media. Other news showed artists winning art competitions with generated art. This creates an interest in detecting which texts or images are AI generated and which ones are real images or human-written texts.

Therefore researchers evaluated different approaches to detect fake images and texts. Some adversarial attacks are already known to be able to reduce the performance of other computer vision tasks, e.g. visual object detection, by artificially manipulating real images.

As this is a very topical issue the "Gesellschaft für Informatik" \cite{GI} organizes a competition called "InformatiCup2024" \cite{InformatiCup} where the participants try to manipulate a detectable source in a way that the detector does not recognize it as AI-generated anymore. This raises the questions, whether and how it is possible to manipulate generated artefacts (e.g. images and texts) to reduce the accuracy of detectors.

@@

\subsection{Generative models}

@@

The \textbf{AIorNot} detector by Nahrawy on Hugging Face is a pretrained swin-tiny-patch4-window7-224 fine-tuned on the AI or Not dataset. Swin-Transformer by Microsoft is a new Vision Transformer which makes use of hierarchical windows. This reduces the self-attention to not-overlapping windows of other areas of the image. \cite{liu2021swin}

@@
